Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
3.4 (FFT part) collapsed into 3.2

\subsection{Fast Whitening and Non-Zero Selection}
\label{sec:fast_whitening}
\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.9\linewidth]{whiten_orig_depth} 
  \end{center}
  \caption{Realistic rendering and depth}
  \label{fig:rendering}
  \end{figure}

@@

@@

\subsection{High Resolution Templates and FFT based Convolution}
\label{sec:fft} 
We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching. These large templates cause computational burden when computing convolution. Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template. To overcome and speed up the convolution, we propose FFT based GPU convolution which scales. Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high resolution template, we can gain computational advantage.

@@

[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]

%------------------------------------------------------------------------

>>>>

\subsection{Fast Whitening and Convolution}
\label{sec:fast_whitening}
\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.9\linewidth]{whiten_orig_depth} 
  \end{center}
  \caption{Realistic rendering and depth}
  \label{fig:rendering}
  \end{figure}

@@

The final challenge in on-the-fly template evaluation is performing the convolution between the template and the target image. Standard convolution would be prohibitively slow for the high resolution templates we're using, so we implemented the convolution via Fast Fourier Transform on the GPU. This allows template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the naive CPU implementation.

@@

\begin{comment}
\subsection{High Resolution Templates and FFT based Convolution}
\label{sec:fft} 
We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching. These large templates cause computational burden when computing convolution. Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template. To overcome and speed up the convolution, we propose FFT based GPU convolution which scales. Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high resolution template, we can gain computational advantage.

@@

[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
\end{comment}
%------------------------------------------------------------------------
